---
title: "CalCOFI Analysis"
subtitle: "for CINMS/MBNMS infographics using ERDDAP"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r}
library(dplyr)
library(purrr)
library(here)
library(fs)
library(glue)
library(sf)
library(mapview)

dir_img <- "/Volumes/GoogleDrive/My Drive/projects/nms-web/cinms/Images"

# functions ----
convert_fig <- function(fig_beg, fig_end, redo=F){
  stopifnot(file.exists(fig_beg), dir.exists(dirname(fig_end)))
  #browser()
  if (!file.exists(fig_end) | redo){
    cmd <- glue("magick convert '{fig_beg}' -resize 800 -alpha on '{fig_end}'")
    system(cmd)
    
    paths_01 <- glue("{path_ext_remove(fig_end)}-{c(0,1)}.png")
    if (all(file.exists(paths_01))){
      file_copy(paths_01[2], fig_end, overwrite = T)
      file_delete(paths_01)
    }
  }
}  

get_nms_ply <- function(nms){
  # eg get_nms_ply("cinms")
  # get polygon for National Marine Sanctuary
  
  nms_shp <- here(glue("data/shp/{nms}_py.shp"))
  
  if (!file.exists(nms_shp)){
    # download if needed
    
    # https://sanctuaries.noaa.gov/library/imast_gis.html
    nms_url <- glue("https://sanctuaries.noaa.gov/library/imast/{nms}_py2.zip")
    nms_zip <- here(glue("data/{nms}.zip"))
    shp_dir <- here("data/shp")
    
    download.file(nms_url, nms_zip)
    unzip(nms_zip, exdir = shp_dir)
    file_delete(nms_zip)
  }
  # read and convert to standard geographic projection
  read_sf(nms_shp) %>%
    st_transform(4326)
}
```


## CINMS Condition Report Figures

### S.LR.12.5. anchovy, sardine, squid in bongo nets

```{r}
figs <- list(
  folder = "State - Living Resources (S.LR.Q#.#)",
  figure = c(
    "S.LR.12.5a_Anchovy_CalCOFI.tif", 
    "S.LR.12.5b_Sardine_CalCOFI.tif", 
    "S.LR.12.5c_Squid_CalCOFI.tif"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))

walk2(figs_beg, figs_end, convert_fig)

knitr::include_graphics(figs_end)
```

Figure S.LR.12.5. Relative abundance of Northern anchovy Engraulis mordax (top), Pacific sardine Sardinops sagax (middle), and market squid Doryteuthis opalescens (bottom) in bongo nets deployed during spring California Cooperative Oceanic Fisheries Investigations (CalCOFI) cruises at sites in the Channel Islands National Marine Sanctuary (CINMS) region from 1978–2015 (except squid collected since 1997). Horizontal lines show the mean (dashed line) ± 1.0 standard deviation (solid lines) over the full time series. Symbol at upper right indicates whether data over the last five years (green shaded areas) had a positive trend (⬈), a negative trend (⬊), or no trend (↔). Symbol at lower right indicates whether the mean over the past five years was greater than (+), less than (–), or within 1 standard deviation (●) of the mean of the full time series. It is important to note that a mean abundance of zero does not mean that the species is completely absent from the waters off of southern California, but that it was not collected at any sites around CINMS during the spring survey that year (sampling locations shown in Appendix F: Figure App.F.12.17). Data source: CalCOFI; Figure: A. Thompson/NMFS SWFSC

### S.LR.15.3 cool/warm-water icthyoplankton, spp richness/diversity

Larval fish in nets

```{r}
figs <- list(
  folder = "State - Living Resources (S.LR.Q#.#)",
  figure = c(
    "S.LR.15.3a_Cool-water.tif", 
    "S.LR.15.3b_warm-water.tif", 
    "S.LR.15.3c_species_richness.tif", 
    "S.LR.15.3d_Simpson_diversity.tif"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))
walk2(figs_beg, figs_end, convert_fig)
knitr::include_graphics(figs_end)
```

Figure S.LR.15.3. (Top) Mean abundance of (left) cool-water associated and (right) warm-water associated ichthyoplankton (larval fishes) collected in net samples during CalCOFI cruises in spring and summer at sites in the Channel Islands National Marine Sanctuary region from 1978 to 2015. (Bottom) The average species richness (left) and species diversity (right) in each net sample is shown for the entire time series. Gini-Simpson diversity (1-λ form) is a measure of the equitability of species in a sample. When individuals are well-distributed among species, Gini-Simpson diversity is high. Graph format is explained in Figure S.LR.12.4. The warm water event also influenced the relative abundance of warm-water species at higher trophic levels including predatory fish, seabirds, and marine mammals. For example, there were increased sightings of species not usually observe

### App.F.12.17 map of net samples

```{r}
figs <- list(
  folder = "App F: LR (AppF.Q#.#)/AppendixF_Q12",
  figure = c(
    "App.F.12.17.Map_CalCOFI.tiff"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))
walk2(figs_beg, figs_end, convert_fig)
knitr::include_graphics(figs_end)
```

Figure App.F.12.17. Location of spring season net samples by the California Cooperative Oceanic Fisheries Investigations (CalCOFI) used in analyses of abundance and trends in pelagic resources in two regions: Channel Islands National Marine Sanctuary region (red) includes CalCOFI stations inside and adjacent to CINMS; and Southern California Shelf (yellow) includes all CalCOFI stations over the shelf. Figure: A. Thompson/NOAA

### App.F.12.18 small plankton volume in CINMS/SoCal

```{r}
figs <- list(
  folder = "App F: LR (AppF.Q#.#)/AppendixF_Q12",
  figure = c(
    "App.F.12.18_CalCOFI_SPV.tiff"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))
walk2(figs_beg, figs_end, convert_fig)
knitr::include_graphics(figs_end)
```

Figure App.F.12.18. Mean volume of small plankton collected in net samples during CalCOFI cruises at only sites in the Channel
Islands National Marine Sanctuary region (top) and all sites over the Southern California Shelf (bottom) from 1978 to 2015 (sampling
locations shown in Figure App.F.12.17). Horizontal lines show the mean (dashed line) ± 1.0 standard deviation (solid lines) over the
full time series. Symbol at upper right indicates whether data over the last five years (green shaded areas) had a positive trend (),
a negative trend (), or no trend (↔). Symbol at lower right indicates whether the mean over the past five years was greater than
(+), less than (–), or within 1 standard deviation (●) of the mean of the full time series..
Figure App.C.4.15. Variation over time in percentage of stations from winter CalCOFI cruises with plastic micro-debris. Micro-debris was present in more than 50 percent of samples at each time period. Figure: Gilfillan et al. 2009

### App.F.12.19 key forage groups in CINMS/SoCal

```{r}
figs <- list(
  folder = "App F: LR (AppF.Q#.#)/AppendixF_Q12",
  figure = c(
    "App.F.12.19b.CalCOFI_Med_ichthy.tiff",
    "App.F.12.19a.CalCOFI_High_ichthy.tiff"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))
walk2(figs_beg, figs_end, convert_fig)
knitr::include_graphics(figs_end)
```

Figure App.F.12.19. Relative abundance of key forage groups collected in net samples during spring CalCOFI cruises at sites in
the Channel Islands National Marine Sanctuary (CINMS) region from 1978 to 2015. Forage is grouped by high (left panel) and
medium (right panel) energy density. High energy taxa are Pacific sardines, northern anchovies, and and Myctophids. Medium-
energy taxa are Pacific hake, shortbelly rockfish, and sanddabs. Although sardine were completely absent in net samples from 2011
to 2014 in the CINMS region, comparison with samples collected in the larger Southern California Shelf region reveal that sardine
were at very low abundance but not completely absent from the region (sampling locations shown in Figure App.F12.17). Symbols
on graph explained in the caption of Figure App.F12.18.
Data source: CalCOFI; Figure: A. Thompson/NOAA

### App.F.12.20 market squid in CINMS/SoCal

```{r}
figs <- list(
  folder = "App F: LR (AppF.Q#.#)/AppendixF_Q12",
  figure = c(
    "App.F.12.20.CalCOFI_squid.tiff"))

figs_beg <- path(dir_img, figs$folder, figs$figure)
figs_end <- here(glue("docs/figures/{path_ext_remove(basename(figs_beg))}.png"))
walk2(figs_beg, figs_end, convert_fig)
knitr::include_graphics(figs_end)
```

Figure App.F.12.20. Mean abundance of market squid (Doryteuthis opalescens) collected in net samples during CalCOFI cruises at
only sites in the Channel Islands National Marine Sanctuary region (top) and all sites over the Southern California Shelf (bottom) from 1997 to 2015 (sampling locations shown in Figure App.F12.17). Symbols on graph explained in the caption of Figure App.F12.18. Data source: CalCOFI; Figure: A. Thompson/NOAA
  
 


## ERDDAP Extraction

- [ERDDAP - Search: calcofi](https://coastwatch.pfeg.noaa.gov/erddap/search/index.html?page=1&itemsPerPage=1000&searchFor=calcofi): 50 matching datasets
- R package [rerddap](https://github.com/ropensci/rerddap)
  - [Using rerddap](https://cran.r-project.org/web/packages/rerddap/vignettes/Using_rerddap.html)
  - [Environmental drivers of small pelagic fish](https://rmendels.github.io/pices2017.nb.html)
  
  
### Spatial filter

```{r}
library(rerddap)
library(lubridate)
library(readr)
#library(tictoc)
here = here::here

d_lrvcntSBtoSC_csv <- here("data/d_lrvcntSBtoSC.csv")

stns <- tabledap('erdCalCOFIstns')
stns <- stns %>% 
  arrange(cruise, ship_code, order_occupied)
#View(stns)

## pull in data taken from erddap
## this file came from the link: CalCOFI Larvae Counts, Scientific Names SB to SC
# see: https://coastwatch.pfeg.noaa.gov/erddap/search/index.html?page=1&itemsPerPage=1000&searchFor=CalCOFI+Larvae+Counts
#raw1 <- read.csv("erdCalCOFIlrvcntSBtoSC_5e28_d9ef_0ecc.csv")

yr_min = 1978
ymd_min = ymd(glue("{yr_min}-01-01"))

p_cinms <- get_nms_ply("cinms")

info("erdCalCOFIlrvcntSBtoSC")
#flds <- c("calcofi_species_code", "station", "line", "longitude", "latitude", "net_location")
#d_lrvcntSBtoSC <- tabledap("erdCalCOFIlrvcntSBtoSC", fields=flds) #%>% 
#tic()


if (!file.exists(d_lrvcntSBtoSC_csv)){
  
  d_lrvcntSBtoSC <- tabledap("erdCalCOFIlrvcntSBtoSC") # 23.3 sec
  #toc()
  # d_lrvcntSBtoSC_0 <- d_lrvcntSBtoSC
  # d_lrvcntSBtoSC <- d_lrvcntSBtoSC_0
  
  d_lrvcntSBtoSC <- d_lrvcntSBtoSC %>% 
    as_tibble() %>% 
    mutate(
      stn_cruise_ship_order = glue("{cruise}-{ship_code}-{order_occupied}"),
      lon   = as.numeric(longitude), # rng: -179.82, -77.23
      lat   = as.numeric(latitude),  # rng:    0.01,  51.09
      dtime = as_datetime(time),
      line_station = glue("{line} {station}")) %>% 
    select(-longitude, -latitude, -time) %>% 
    filter(
      dtime        >= ymd_min,          # n: 2,416,384 -> 1,501,280
      # select only starboard samples from the bongo nets
      net_location == "starboard") %>%  # n: 2,416,384 -> 1,792,640
    arrange(cruise, ship_code, order_occupied) #  x 25
  
  # core stations
  linestation_core = c(
    "76.7 49", "76.7 51", "76.7 55", "76.7 60","76.7 70","76.7 80","76.7 90", "76.7 100","80 51",
    "80 55","80 60","80 70","80 80", "80 90","80 100",
    "81.8 46.9","83.3 40.6", "83.3 42", "83.3 51", "83.3 55", "83.3 60","83.3 70","83.3 80", "83.3 90", "83.3 100","83.3 110",
    "86.7 33", "86.7 35", "86.7 40", "86.7 45", "86.7 50", "86.7 55","86.7 60","86.7 70", "86.7 80", "86.7 90", "86.7 100", "86.7 110",
    "90 28", "90 30", "90 35","90 37", "90 45", "90 53", "90 60", "90 70", "90 80", "90 90", "90 100", "90 110", "90 120",
    "93.3 26.7", "93.3 28", "93.3 30", "93.3 35", "93.3 40","93.3 45", "93.3 50","93.3 60","93.3 70", "93.3 80", "93.3 90", "93.3 100","93.3 110","93.3 120")
  
  # CINMS stations
  linestation_cinms = c(
    "76.7 49", "76.7 51", "76.7 55", "76.7 60","80 51", "80 55", 
    "80 60","81.8 46.9","83.3 40.6", "83.3 42", "83.3 51", "83.3 55", "83.3 60",
    "86.7 33", "86.7 35", "86.7 40", "86.7 45", "86.7 50", "86.7 55","86.7 60","90 28", "90 30", "90 35",
    "90 37", "90 45", "90 53","90 60", "93.3 26.7", "93.3 28", "93.3 30", "93.3 35", "93.3 40",
    "93.3 45", "93.3 50","93.3 60")
  
  # SB stations
  linestation_sb <- c("80 55","80 51","81.8 46.9","83.3 55","83.3 51","83.3 42","83.3 40.6")
  
  d_lrvcntSBtoSC <- d_lrvcntSBtoSC %>% 
    mutate(
      is_core  = line_station %in% linestation_core,
      is_cinms = line_station %in% linestation_cinms,
      is_sb    = line_station %in% linestation_sb)
  #d_lrvcntSBtoSC %>% head(1000) %>% View()
  
  write_csv(d_lrvcntSBtoSC, d_lrvcntSBtoSC_csv)
} else {
  d_lrvcntSBtoSC <- read_csv(d_lrvcntSBtoSC_csv)
}


p_stns <- d_lrvcntSBtoSC %>% 
  filter(is_core) %>% 
  group_by(stn_cruise_ship_order) %>% 
  summarise(
    lon          = mean(lon),
    lat          = mean(lat),
    line_station = first(line_station),
    is_core      = first(is_core),
    is_cinms     = first(is_cinms),
    is_sb        = first(is_sb)) %>% 
  st_as_sf(coords=c("lon", "lat"), crs=4326, remove=F)

hul_cinms <- d_lrvcntSBtoSC %>% 
  filter(is_cinms) %>% 
  st_as_sf(coords=c("lon", "lat"), crs=4326, remove=F) %>% 
  st_union() %>% st_convex_hull()

hul_core <- p_stns %>% 
  filter(is_core) %>% 
  st_union() %>% st_convex_hull()

hul_sb <- p_stns %>% 
  filter(is_sb) %>% 
  st_union() %>% st_convex_hull()

cols_fill <- sf.colors(n=3, alpha=0.3)
cols_brdr <- sf.colors(n=3, alpha=0.6)
plot(st_geometry(hul_core) , col=cols_fill[1], border = cols_brdr[1], axes=T)
plot(st_geometry(hul_cinms), col=cols_fill[2], border = cols_brdr[2], add = T)
plot(st_geometry(hul_sb)   , col=cols_fill[3], border = cols_brdr[3], add = T)
plot(st_geometry(p_stns %>% filter(is_core)) , col=cols_fill[1], add=T)
plot(st_geometry(p_stns %>% filter(is_cinms)), col="blue", add=T)
plot(st_geometry(p_stns %>% filter(is_sb))   , col="red" , add=T)
legend("bottomright", 
  legend  = c("Core", "CINMS", "Santa Barbara"), 
  fill    = cols_fill,
  border  = cols_brdr) #, bty="n")
```


#### old spatial 
```{r eval=F}
ply <- mapedit::editFeatures(p_stns %>% filter(is_core))
mapview::mapview(ply)

p_stns3 %>% filter(is_cinms)

plot(st_geometry(p_stns3 %>% )   , col="red", axes=T) # , add=T)


names(d_lrvcntSBtoSC)
summary(d_lrvcntSBtoSC %>% select(lon, lat))

d_lrvcntSBtoSC$line
d_lrvcntSBtoSC$station

### select just the core stations
raw3 <- subset(raw2, line.station %in% c("76.7 49", "76.7 51", "76.7 55", "76.7 60","76.7 70","76.7 80","76.7 90", "76.7 100","80 51", 
											"80 55","80 60","80 70","80 80", "80 90","80 100",
											"81.8 46.9","83.3 40.6", "83.3 42", "83.3 51", "83.3 55", "83.3 60","83.3 70","83.3 80", "83.3 90", "83.3 100","83.3 110", 
							"86.7 33", "86.7 35", "86.7 40", "86.7 45", "86.7 50", "86.7 55","86.7 60","86.7 70", "86.7 80", "86.7 90", "86.7 100", "86.7 110",
							"90 28", "90 30", "90 35","90 37", "90 45", "90 53", "90 60", "90 70", "90 80", "90 90", "90 100", "90 110", "90 120",
							"93.3 26.7", "93.3 28", "93.3 30", "93.3 35", "93.3 40","93.3 45", "93.3 50","93.3 60","93.3 70", "93.3 80", "93.3 90", "93.3 100","93.3 110","93.3 120"))




# head(d_lrvcntSBtoSC) %>% View()
d_lrvcntSBtoSC$dtime[1] > 
  
  year(yr_min)

lubridate::as_datetime(d_lrvcntSBtoSC$time[1])
d_lrvcntSBtoSC$
time

# check lat/lon differences per station
# stns2 <- d_lrvcntSBtoSC %>%
#   group_by(stn_cruise_ship_order) %>% # n: 50,161
#   summarise(
#     lon_avg = mean(lon),
#     lon_min = min(lon),
#     lon_max = max(lon),
#     lon_dif = lon_max - lon_min,
#     lat_avg = mean(lat),
#     lat_min = min(lat),
#     lat_max = max(lat),
#     lat_dif = lat_max - lat_min) %>%
#   arrange(desc(lat_dif))
# stns2 # OK: 0 for lat_dif, lon_dif




p_stns2 <- d_lrvcntSBtoSC %>% 
  group_by(stn_cruise_ship_order) %>% 
  summarise(
    lon = first(lon),
    lat = first(lat)) %>% 
  st_as_sf(
    coords = c("lon", "lat"), 
    crs = 4326, remove = F)

plot(st_geometry(p_stns2), reset=F, axes=T, key.pos=NULL)
plot(st_geometry(p_stns2), reset=F, axes=T, key.pos=NULL)
plot(p_cinms['AREA_NAME'],   add=T)
plot(p_cinms['AREA_NAME'], axes=T, key.pos=NULL)
plot()

head(d_lrvcntSBtoSC)
  
  View()
d_lrvcntSBtoSC <- d_lrvcntSBtoSC %>% 
  
summary(d_lrvcntSBtoSC)

stns <- d_lrvcntSBtoSC %>% 
  group_by(station, line) %>% 
  summarize(
    lon_mean = mean(lon),
    lon_min  = min(lon),
    lon_max  = max(lon),
    lon_dif  = lon_max - lon_min,
    lat_mean = mean(lat),
    lat_min  = min(lat),
    lat_max  = max(lat),
    lat_dif  = lat_max - lat_min)
View(stns)
View(d_lrvcntSBtoSC)

# TODO: throw warnings() about species not in ERDDAP selected area 
#       and display species that are in the area but not selected.
# GOAL: to be able to update the CINMS CR/infographic in future years
#          for similar taxa and sites (ie within selected polygon)
#      and to perform similar analyses in other regions, ie:
#          MBNMS, OCNMS, CA Current IEA
# CalCOFI now mostly SoCal, except Line 67 in Monterey
#  

datasets <- ed_search(query = "CalCOFI", which = "tabledap")
datasets

info()


#mapview::mapview(p_cinms)

st_join(pts, poly, join = st_intersects)

summary(d_lrvcntSBtoSC)

p_lrvcntSBtoSC <- st_as_sf(d_lrvcntSBtoSC, coords = c("lon", "lat"), crs = 4326)
p_stns <- st_as_sf(stns, coords = c("lon_mean", "lat_mean"), crs = 4326)

p_lrvcntSBtoSC <- st_join(p_lrvcntSBtoSC, select(p_cinms, SANCTUARY))


table(p_lrvcntSBtoSC$SANCTUARY, useNA="always")

plot(p_cinms["SANCTUARY"])
plot(p_cinms[1])
plot(p_lrvcntSBtoSC[1], add=T)

mapview(p_cinms) + mapview(p_lrvcntSBtoSC)
mapview(p_cinms) + mapview(p_lrvcntSBtoSC %>% filter(SANCTUARY=="CINMS")

sf::st_covered_by()
```

### Taxa filter

```{r}
d_lrvcntSBtoSC %>% 
  filter(is_cinms) %>% 
  select(scientific_name) %>% 
  table()
```


Need to access other ERDDAP endpoints to get species of interest:

- Northern anchovy (_Engraulis mordax_)
- Pacific sardine (_Sardinops sagax_)
- market squid (_Doryteuthis opalescens_)

### TODO: check `cruise_shipcode`

```{r, eval=F}
raw5 <- subset(raw4,cruise_shipcode %in% c("201504 NH","201404 OS","201402 SH","201304 SH","201307 NH","201301 SH",
"201210 NH","201203 SH","201207 OS","201202 NH","201110 NH","201104 SH","201108 NH","201101 NH","201011 NH","201004 MF",
"201008 NH","201001 NH","200911 NH","200903 JD","200907 M2","200901 NH","200810 NH","200804 JD","200808 NH","200801 JD",
"200711 NH","200704 JD","200707 NH","200701 JD","200610 RR","200604 NH","200607 NH","200602 JD","200511 NH","200504 NH",
"200507 NH","200501 NH","200411 RR","200404 NH","200407 JD","200401 JD","200310 NH","200304 RR","200307 NH","200302 JD",
"200211 NH","200204 JD","200207 NH","200201 JD","200110 NH","200104 JD","200107 NH","200101 JD","200010 NH","200004 JD",
"200007 NH","200001 NH","199910 NH","199904 JD","199908 NH","199901 RR","199809 NH","199804 JD","199807 NH","199802 JD",
"199709 NH","199704 NH","199707 JD","199702 JD","199610 RR","199604 JD","199608 NH","199602 JD","199510 NH","199504 NH",
"199507 JD","199501 JD","199410 NH","199403 JD","199408 NH","199401 JD","199310 NH","199304 JD","199308 NH","199301 JD",
"199210 NH","199204 JD","199207 JD","199202 JD","199110 NH","199103 JD","199108 JD","199101 JD","199011 NH","199003 JD",
"199008 NH","198911 NH","198904 JD","198907 NH","198901 JD","198810 NH","198805 JD","198808 NH","198801 JD","198711 NH",
"198705 JD","198709 NH","198703 JD","198611 NH","198605 JD","198609 NH","198602 JD","198511 NH","198505 JD","198508 NH",
"198502 M4","198410 JD","198410 NH","198404 JD","198404 NH","198407 JD","198407 NH","198401 JD","198401 NH","198303 EK",
"198104 JD","198107 JD","198101 JD","197803 JD","197807 JD","197801 JD","197511 JD","197505 JD","197507 JD","197501 AX",
"197501 JD","197207 AL","197207 AX","197207 JD","197202 AX","197202 AB","197202 AL","196910 JD","196904 JD","196907 JD",
"196901 JD","196806 JD","196801 HO","196706 EB","196610 JD","196604 AL","196607 JD","196602 AX","196509 BD","196504 AX",
"196507 AX","196507 BD","196501 AX","196501 BD","196410 BD","196404 AX","196407 AX","196407 BD","196401 AX","196401 BD",
"196310 BD","196304 AX","196304 BD","196307 BD","196301 AX","196301 BD","196210 AX","196210 BD","196203 HO","196203 BD",
"196207 BD","196201 HO","196201 BD","196110 HO","196110 BD","196104 HO","196104 BD","196107 HO","196107 BD","196101 HO",
"196101 BD","196010 BD","196010 SB","196004 HO","196004 HS","196007 HO","196007 BD","196002 BD","195910 SB","195910 OR",
"195904 OR","195907 OR","195907 PT","195901 BD","195901 OR","195810 ST","195804 SB","195804 BD","195804 PT","195807 PT",
"195807 OR","195710 PT","195704 HO","195707 ST","195707 PT","195604 ST","195607 OR","195607 PT","195504 CR","195507 CR",
"195507 PT","195404 HO","195404 ES","195406 HO","195304 HO","195304 PT","195304 CR","195306 CR","195306 ES","195306 YE",
"195306 PT","195204 HO","195204 CR","195206 SB","195206 BD","195206 YE","195104 BD","195104 CR","195106 BD","195106 YE",
"195101 47","195101 CR"))
```

